---
title: "Capstone Project-How Can a Wellness Technology Company Play It Smart?"
author: "Jayanthi Manickam Sethu"
date: "2022-10-24"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### This is my **Google Capstone Project**. My first data analysis project in R

**Stakeholders**<BR/>
**Urška Sršen**: Bellabeat’s cofounder and Chief Creative Officer<BR/>
**Sando Mur**: Mathematician and Bellabeat’s cofounder; key member of the Bellabeat executive team
<BR/>
This analysis answers to the below questions

* What are some trends in smart device usage?
* How could these trends apply to Bellabeat customers?
* How could these trends help influence Bellabeat marketing strategy?

**Business Task** </BR>
To deduct the trend of smart devices usage and give recommendations to improve the Bellabeat app

<BR/>
**Process** <BR/>
Before starting to load the files through R. I did some cleaning in the data files.

* The date format across the files was not consistent.So converted Non date dates through Data->Text to columns and formatted the date.
* I did a VLOOKUP and merged data from 2 CSV files-Got the calories data and merged in daily steps data
* There was no data for water intake. So I took data from <https://www.worldometers.info/water/>. It gives details about Water intake across the countries.
<BR/>

**Installing the necessary packages**
```{r Installing the necessary packages}
      
      library(tidyverse)
      library(lubridate)
      library(ggplot2)
      library(dplyr)
      library(grid)
      library(ggpmisc)
```

** Set the working directory **
```{r 
```


**Read CSV Files**

```{r  Set the working Directory and Read CSV files}
      
      # Set current working directory.
      setwd("C:/Users/Jay/OneDrive/Jay Study/Google data analytics/Capstone Project/Data/Fitabase Data 4.12.16-5.12.16")
      
      # Get and print current working directory.
      print(getwd())
      
      sleepData <- read.csv("sleepDay_merged.csv")
      print(is.data.frame(sleepData))
      print(ncol(sleepData))
      print(nrow(sleepData))
      head(sleepData)
      totalTimeTakentoSleep <- sleepData %>% 
                       group_by(Id,SleepDay) %>% 
                       summarise(TimeTakenToSleep = sum(TimeTakenToSleep))%>%
                       arrange(desc(TimeTakenToSleep))
      print(ncol(totalTimeTakentoSleep))
      print(nrow(totalTimeTakentoSleep))
      head(totalTimeTakentoSleep)

      #topTimeTakentoSleep <-head(totalTimeTakentoSleep, 5)

      # print(ncol(topTimeTakentoSleep))
      # print(nrow(topTimeTakentoSleep))
      # head(topTimeTakentoSleep)
      
      waterIntakeData <- read.csv("world_water_intake.csv")
      print(is.data.frame(waterIntakeData))
      print(ncol(waterIntakeData))
      print(nrow(waterIntakeData))
      head(waterIntakeData)
      

      topwaterIntake <- head(waterIntakeData,5)
      

      print(ncol(topwaterIntake))
      print(nrow(topwaterIntake))
      head(topwaterIntake)

      calorieData <- read.csv("weightLogInfo_merged.csv")
      print(is.data.frame(calorieData))
      print(ncol(calorieData))
      print(nrow(calorieData))
      head(calorieData)
      # filterCalorieData <-calorieData %>% group_by(Id) %>%
      #                     summarise(max_WeightKg=max(WeightKg))
      # head(filterCalorieData)
      
      calorieStepsData <- read.csv("dailySteps_merged.csv")
      print(is.data.frame(calorieStepsData))
      print(ncol(calorieStepsData))
      print(nrow(calorieStepsData))
      head(calorieStepsData)
      
```
** Scatter Plot for Sleep pattern **
```{r}
ggplot(data = totalTimeTakentoSleep) +
  geom_point(mapping = aes(x =SleepDay,y= TimeTakenToSleep),color="purple")+
  ggtitle("Time Taken to sleep each day")

ggplot(data = topwaterIntake,aes(Country, YearlyWaterUsed)) +
  geom_point() +
  annotate(geom = "table",
           x = 9,
           y = 3,
           label = list(topwaterIntake))+
  ggtitle("Water Intake of Top 5 populated Countries")

# ggplot(data = calorieStepsData,aes(x=StepTotal,y=TotalCaloriesBurnt)) +
#  geom_boxplot(outlier.colour="red", outlier.shape=8,
#                 outlier.size=4)

ggplot(data = calorieStepsData) + 
  geom_point(mapping = aes(x = StepTotal,y = TotalCaloriesBurnt,color=Id))+
  ggtitle("Steps walked vs Calories Burnt")
  # facet_wrap(~Id)


ggplot(data = calorieData,aes(x=WeightKg,y=BMIStatus)) +
          geom_violin()+
  ggtitle("Weight vs BMI")
  



 

```
</BR></BR>**Recommendations**</BR>

* In the smart devices, there is a feature to set reminder to drink water but if there is a feature in app to enter the measures of water intake every time the user drinks. By end of the day,the user can know the status of water intake with a status-Normal,More or Less intake. 

* Should there be a provision to enter weight weekly or monthly and track BMI indicating Overweight or Normal







